---
title: "ANLY 506 - EDA Final Project"
author: "Ly Dang"
date: "June 09, 2019"
output:
  html_document:
    code_folding: hide
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## I. Questions to ask

1. Which countries have the largest population?
2. Which countries have the largest income?
3. Is there a possible relationship between income and life?


## II. Loading libraries:

```{r}
library(igraph)
library(reshape2)
library(dplyr)
library(readxl)
library(zoo)
library(NbClust)
library (cluster)
library (clustertend)
library (factoextra)
library(tidyverse)
library(ggplot2)

```


## III. Describe data

2. Describe your data 10 pts

Overall narrative summary of data:
       
life = life expectancy
income = gdp per capita
year
country
region
population - census data collected about every 10 years

o   41,284 observations

o   6 variables

o   type of variables 
Country   : chr  
Year      : int  
life      : num  
population: num  
income    : int  
region    : chr  

o   how disperse is your data 
life: range = max - min = 84.1 - 1 = 83.1
year: range = 2015 - 1800 = 215 years


o   data wrangling 
In gapminder population is calculated every ten years. Thus the same # population is applied to every year during the 10 year period. Perform data wrangling to treat missing ppopulation value the same as the lates non-missing value.

o  preprocessing steps 

Other than that, I don't do other preprocessing steps such as normalizing data because it's data exploration so there is no assumption to be satisfied as in hypothesis testing.


```{r}

library(readr)
gapminder <- read_csv("~/A-HU CPT/ANLY 506/gapminder.csv")
gapminder$population <- na.locf(gapminder$population)

summary(gapminder)
str(gapminder)
gapminder1 <- na.omit(gapminder)
tail(gapminder1)



````


## IV. Explore data

#### Density graph showing life and income relationship:

```{r}

ggplot(data = gapminder1) + 
  geom_point(aes(x = income, y = population, size = 3, shape = '24',colour = 'black')) +labs(title="Graph 1: life by income",y="Count",x="life") 


````

#### Life distribution

```{r}
d <- density(gapminder1$life)
plot(d, type="n", main="life distribution")
polygon(d, col="lightgray", border="gray")
rug(gapminder1$life, col="red")
````

#### Data visualization
```{r}

ggplot(data = gapminder1) + 
  geom_point(aes(x = income, y = population, size = 3, shape = '24',colour = 'black'))

````


#### Calculate distance life and income
```{r}
library(knitr)
fm <- matrix(c(gapminder1$income,gapminder1$life), byrow = T, nrow = 2)
fm
dist(fm)

````

#### Evaluate the best number of clusters using gap method. 
```{r}
fviz_nbclust(gapminder1, kmeans, method = "gap_stat")+ theme_classic()     

````


##. V. Conclustion
1, There is little relationship between life and income
2. life doesn't have a normal distribution


## III. Reference

1. The Art of Data Science - Roger D, Peng and Elizabeth Matsui
2. UC Berkeley R programming Guide
.
