---
title: "ANLY 506 - Code Portfolio"
author: "Ly Dang"
date: "June 09, 2019"
output:
  pdf_document: default
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## I. Introduction

Code portfolio summarizing weekly coding practice 


## II. Code porfolio:

```{r}
library(igraph)
library(reshape2)
library(dplyr)
library(readxl)

```


#### Exploratory Data Analysis

```{r}
library('readr')
ozone <- read_csv("~/A-HU CPT/ANLY 506/US EPA data 2017.csv")
str(ozone)
summary(ozone)
head(ozone, n = 10)

````


#### Importing, saving and managing data

```{r}
library(tidyverse)
names(ozone) <- make.names(names(ozone))
select(ozone, State.Name) %>% unique %>% nrow
unique(ozone$State.Name)

x <- c(15,20,50,70,80,95)
x[c(2,6)]
x[-5]

filter(starwars, species == "Human")
library(readr)
income <- read_csv("~/A-HU CPT/ANLY 506/income.csv")
mean(income$M_weekly)
mean(income$M_weekly)
mean(income$M_weekly,trim = 0.1, na.rm = TRUE)
median(income$M_weekly,trim = 0, na.rm = TRUE)

````
#### Practical stats


```{r}
library(matrixStats)
weighted.mean(income$M_weekly,w=income$Industry,na.rm = TRUE)
weighted_median <- function(M_weekly, Industry,na.rm = TRUE)
{
  
  if(na.rm){
    
    df_omit <- na.omit(data.frame(M_weekly, Industry))
    
    return(weightedMedian(df_omit$M_weekly, df_omit$Industry,na.rm = TRUE))
    
  } 
  
  weightedMedian(M_weekly, Industry,na.rm = TRUE)
  
}
weighted_median(income$M_weekly,income$Industry,na.rm = TRUE)
sd(income$F_workers)
mad(income$F_workers)
iqr(income$F_workers)
names(ozone) <- make.names(names(ozone))
select(ozone, State.Name) %>% unique %>% nrow
unique(ozone$State.Name)
sd(mtcars[["mpg"]])

IQR(mtcars[["mpg"]])

mad(mtcars[["mpg"]])

````

#### Data transformation

```{r}
library(dplyr)
library(tibble)
income <- as.tibble(income)
income1 <- filter(income, M_weekly > 2000)
str(income1)
head(income1)
library(nycflights13)
data('flights')
str(flights)
flights1 <- filter(flights, day == "30", month == "12")
flights2 <- filter(flights1, dep_delay == "NA")
summary(flights2)
head(flights2)
flights3 <- filter(flights, dep_delay == "NULL")
mean(flights1$dep_delay,na.rm = TRUE)
head(flights2)

income1 <- mutate(income,diff = M_weekly - F_weekly)
income1 %>% glimpse()
sd <- sd(income1$diff,na.rm = TRUE)
round(sd, 2)

library(tidyverse)
data("iris")
str(iris)
summary(iris)
iris2<-iris %>%
  
  filter(Petal.Length > 4.5)
iris3<-iris2 %>%
  
  filter(Species=="virginica")
summary(iris3)
````

#### Data visualization
```{r}
data("faithful")
summary(faithful)
data(who)
str(who)
summary(who)
head(who)
ggplot(data = mpg) + 
  geom_point(aes(x = displ, y = hwy, size = 3, shape = '24',colour = 'black'))

````
#### Create Data frame

```{r}
Age <- c(22, 25, 18, 20)
Name <- c("James", "Mathew", "Olivia", "Stella")
Gender <- c("M", "M", "F", "F")
DataFrame = data.frame(c(Age), c(Name), c(Gender))
subset(DataFrame, Gender == "M")
DataFrame = data.frame(Age,Name,Gender)
subset(DataFrame,Gender=="M")
data(AirPassengers)
AirPassengers[AirPassengers >= 1949 & AirPassengers < 1950]
AirPassengers[time(AirPassengers) >= 1949 & time(AirPassengers) < 1950]

p <- c(2,7,8)
q <- c("A", "B", "C")
x <- list(p, q)
x[2]
w <- c(2, 7, 8)
v <- c("A", "B", "C")
x <- list(w, v)
x
x[[2]] <- "K" 
x
x[[2]][1] <- "K" 
x
x[[1]][2] <- "K"
x
a <- list ("x"=5, "y"=10, "z"=15)

y <- list("a", "b", "c")
data1 <- data.frame(id=c("ID.1", "ID.2", "ID.3"))
sample1=c(5.01, 79.40, 80.37)
sample2=c(5.12, 81.42, 83.12)
sample3=c(8.62, 81.29, 85.92)

```  

#### Calculate distance
```{r}
library(knitr)
fa <- c(3, 4, 7, 8)
fb <- c(5, 7, 7, 6)
fm <- matrix(c(fa,fb), byrow = T, nrow = 2)
fm
dist(fm)

````

#### Evaluate the best number of clusters using gap method. 
```{r}

library(NbClust)
          
library (cluster)
          
library (clustertend)
          
library (factoextra)

Cluster1 <- read.table("~/A-HU CPT/ANLY 506/Cluster 1.txt", quote="\"", comment.char="")
View(Cluster1)
Cluster2 <- read.table("~/A-HU CPT/ANLY 506/Cluster 2.txt", quote="\"", comment.char="")
View(Cluster2)
Cluster3 <- read.table("~/A-HU CPT/ANLY 506/Cluster 3.txt", quote="\"", comment.char="")
View(Cluster3)
clusters <- data.frame(Cluster1, Cluster2, Cluster3)
names(clusters) <- c("c1", "c2", "c3")
View(clusters)
clusters <- clusters[, c(2, 4, 6)]
fviz_nbclust(clusters, kmeans, method = "gap_stat")+ theme_classic()     

````


#### Perform agglomerative clustering
```{r}
df <- USArrests
df <- na.omit(df)
df <- scale(df)
head(df)
d <- dist(df, method = "euclidean")
hc2 <- agnes(df, method = "complete")
hc2$ac
ac <- function(x) {agnes(df, method = x)$ac}
m <- c( "average", "single", "complete", "ward")
names(m) <- c( "average", "single", "complete", "ward")
map_dbl(m, ac)

````

## III. Reference

1. The Art of Data Science - Roger D, Peng and Elizabeth Matsui
2. UC Berkeley R programming Guide
.
